\Title

### 2023-06-01 Grimaldi-etal-BiolCybernetics.tex
Results : A

If one focuses on the interpretation of these kernels in terms of spatio-temporal motifs embedded in the event stream, it can lead to interesting outcomes. In~\citep{grimaldi_robust_2022}, a link between event-based MLR training and Hebbian learning is drawn, allowing to say that the present model will learn its weights according to a presynaptic activity associated to the different motion directions. Each neuron becomes selective to a specific motion direction through the learning of an associated prototypical spatio-temporal spiking motif. Each voxel in the 3D kernels defines a specific timestamp and a specific address. Consequently, our model is able to detect precise spatio-temporal motifs embedded in the spike train and associated to the different motion directions. The cone shape for the positive weights' distribution highlights a loss of precision for longer delays, i.e. events away in the past. %For the directions not coherent to the class of a training sample, an anti-Hebbian learning is also observed through the negative weights in the kernels of Fig.~\ref{fig:kernels}.

%
% \note{kernel size has to be adapted to the characteristics of motion see Samonds %~\citep{samonds}
% say that we have tested }
% \note{tester la meme expe faite par baudot et modelisée par kremkow en montrant des raster plots du modele avec NI versus Gratings }

%%%-----------------------------------------------------------------
%
\subsection{Testing with natural-like textures}
%%%-----------------------------------------------------------------
%%%-----------------------------------------------------------------
%: fig:motion_clouds
%%%-----------------------------------------------------------------
\begin{figure}%[h!]
    \centering
    \includegraphics[width=0.99\linewidth]{figures/motion_clouds.pdf} %
    \caption{{\bf Role of stimulus parameters in the motion detection accuracy.} Accuracy as a function of (from left to right) the mean spatial frequency, the bandwidth in spatial frequency (from a grating-like (left) to isotropic textures (right)), the bandwidth in orientation (from isotropic textures (left) to grating-like (right)), the bandwidth in speed (from a rigid motion (left) to independent frames (right)). Note that these accuracies are computed both in the case where orientation of the synthetic texture is necessarily perpendicular to the motion ('no aperture' condition) or in the generic case where orientation is independent of direction ('aperture').}
    \label{fig:motion_clouds}
\end{figure}
%%%-----------------------------------------------------------------
To test our model, we will quantify its ability to categorize different motions, that is on event streams for which the ground truth motion is known at every instant in time. Before applying the model on natural images, we will first test the model on simpler, parameterized stimuli. In that order, we use a set of synthetic visual stimuli, \textit{Motion Clouds}~\citep{leon_motion_2012} which are natural-like random textures for which we can control for motion, among other parameters (\seeFig{motion_clouds})~\citep{vacher_bayesian_2018}. In particular, we will set the spatial extent and duration of the generated movies similarly to the motion task defined above. This procedure defines a set of textures with different spatial properties and different motions picked from the same set of $8$ directions and $3$ speeds. For any given motion, we also varied the parameters of the textures, such as the mean and variance of the orientation or spatial frequency content to provide with some naturalistic variability. This method provides a rich dataset of textured movies for which we know the ground truth for motion.

>>>>

If one focuses on the interpretation of these kernels in terms of spatio-temporal motifs embedded in the event stream, it can lead to interesting outcomes. In~\citep{grimaldi_robust_2022}, a link between event-based MLR training and Hebbian learning is drawn, allowing to say that the present model will learn its weights according to a presynaptic activity associated to the different motion directions. Each neuron becomes selective to a specific motion direction through the learning of an associated prototypical spatio-temporal spiking motif. Each voxel in the 3D kernels defines a specific timestamp and a specific address. Consequently, our model is able to detect precise spatio-temporal motifs embedded in the spike train and associated to the different motion directions. The cone shape for the positive weights' distribution highlights a loss of precision for longer delays, i.e. events away in the past. 
%
%%%-----------------------------------------------------------------
%
\subsection{Testing with natural-like textures}
%%%-----------------------------------------------------------------
%%%-----------------------------------------------------------------
%: fig:motion_clouds
%%%-----------------------------------------------------------------
\begin{figure}%[h!]
    \centering
    \includegraphics[width=0.99\linewidth]{figures/motion_clouds.pdf} %
    \caption{{\bf Role of stimulus parameters in motion detection accuracy.} Accuracy as a function of (from left to right) mean spatial frequency, bandwidth in spatial frequency (from a grating (left) to isotropic textures (right)), bandwidth in orientation (from isotropic textures (left) to grating (right)), bandwidth in speed (from a rigid motion (left) to independent frames (right)). Note that these accuracies are computed both in the case where the orientation of the synthetic texture is necessarily perpendicular to the motion ('no aperture' condition) and in the generic case where the orientation is independent of direction ('aperture').
    }
    \label{fig:motion_clouds}
\end{figure}
%%%-----------------------------------------------------------------
To further test our model, we will quantify its ability to categorize different motions, that is on event streams for which the ground truth motion is known at every instant in time. Before applying the model on natural images, we will first test the model on simpler, parameterized stimuli. In that order, we use a set of synthetic visual stimuli, \textit{Motion Clouds}~\citep{leon_motion_2012} which are natural-like random textures for which we can control for motion, among other parameters (\seeFig{motion_clouds})~\citep{vacher_bayesian_2018}. In particular, we will set the spatial extent and duration of the generated movies similarly to the motion task defined above. This procedure defines a set of textures with different spatial properties and different motions picked from the same set of $8$ directions and $3$ speeds. For any given motion, we also varied the parameters of the textures, such as the mean and variance of the orientation or spatial frequency content to provide with some naturalistic variability. This method provides a rich dataset of textured movies for which we know the ground truth for motion.
